A Short and Mechanized Consistency Proof for Dependent Type Theory

### 2023-12-30 paper/paper.tex
Add figure for semantic typing

\section{Semantic Typing and Consistency}
\label{sec:logrelproof}
The logical relation we define in Figure~\ref{fig:logrel} does not
include cases for variables. Likewise, for the base types such as
boolean and equality, the output set $[[S]]$ contains only terms that
evaluate to closed terms. To generalize our logical relation to open
terms, we define the semantic typing judgment by closing the open
terms with a substitution whose codomain consists of terms that
respect the interpretation of the types from the context. The full
definition of semantic typing ($[[ G |= a : A]]$) is presented in
Figure~\ref{fig:semtyping}.

>>>>

\section{Semantic Typing and Consistency}
\label{sec:logrelproof}
\begin{figure}[h]
  \begin{equation*}
    \begin{split}
      [[rho |= G]] &:= \forall i\ j\ S, \text{ if }[[i < |G|]]\text{ and
                     } [[InterpR j (up S i G i) { rho } S ]] \text{, then } [[rho i in S]] \\
      [[G |= a : A]] &:= \forall [[rho]], \text{ if }[[rho |=
                       G]]\text{ then there exists some } [[j]] \text{
                       and } [[S]] \text{ such that } [[InterpR j A
                       {rho} S]] \text{ and } [[a {rho} in S]] \\
      [[|= G]] &:= \forall [[i < |G|]], \exists [[j]], [[drop S i G |= G i : Set j]]
    \end{split}
  \end{equation*}
  \caption{Semantic Typing for \lang}
  \label{fig:semtyping}
\end{figure}

The logical relation we define in Figure~\ref{fig:logrel} does not
include cases for variables. Likewise, for the base types such as
boolean and equality, the output set $[[S]]$ contains only terms that
evaluate to closed terms. To generalize our logical relation to open
terms, we define the semantic typing judgment by closing the open
terms with a substitution whose codomain consists of terms that
respect the interpretation of the types from the context. The full
definitions of well-formed substitution ($[[rho |= G]]$), semantic
typing ($[[ G |= a : A]]$), and semantic context well-formedness
($[[|= G]]$) are presented in Figure~\ref{fig:semtyping}.

Next, we show that semantic typing is implied by syntactic typing
case-by-case through a series of lemmas.

\begin{lemma}[ST-Var]
  If $[[|= G]]$ and $[[i < |G|]]$, then $[[G |= i : up S i G i]]$.
\end{lemma}

\begin{lemma}[ST-Set]
  If $[[|= G]]$ and $[[i < j]]$, then $[[G |= Set i : Set j]]$.
\end{lemma}

\begin{lemma}[ST-Pi]
  If $[[G |= A : Set i]]$ and $[[G ++ A |= B : Set i]]$, then $[[G |= Pi
  A B : Set i]]$.
\end{lemma}
